Richard Yuanzhe Pang, Alicia Parrish, Nitish Joshi, Nikita Nangia, Jason Phang, Angelica Chen, Vishakh Padmakumar, Johnny Ma, Jana Thompson, \textbf{He He} and Sam Bowman. {QuALITY}: Question Answering with Long Input Texts, Yes!. \textit{North American Chapter of the Association for Computational Linguistics (NAACL)}, 2022.

Vishakh Padmakumar, Leonard Lausen, Miguel Ballesteros, Sheng Zha, \textbf{He He} and George Karypis. Exploring the Role of Task Transferability in Large-Scale Multi-Task Learning. \textit{North American Chapter of the Association for Computational Linguistics (NAACL)}, 2022.

Vishakh Padmakumar and \textbf{He He}. Machine-in-the-Loop Rewriting for Creative Image Captioning. \textit{North American Chapter of the Association for Computational Linguistics (NAACL)}, 2022.

Yanda Chen, Ruiqi Zhong, Sheng Zha, George Karypis and \textbf{He He}. Meta-learning via Language Model In-context Tuning. \textit{Association for Computational Linguistics (ACL)}, 2022.

Faisal Ladhak, Esin Durmus, \textbf{He He}, Claire Cardie and Kathleen McKeown. Faithful or Extractive? On Mitigating the Faithfulness-Abstractiveness Trade-off in Abstractive Summarization. \textit{Association for Computational Linguistics (ACL)}, 2022.

Nitish Joshi and \textbf{He He}. An Investigation of the (In)effectiveness of Counterfactually Augmented Data. \textit{Association for Computational Linguistics (ACL)}, 2022.

Yana Dranker, \textbf{He He} and Yonatan Belinkov. {IRM} - When It Works and When It Doesn't: A Test Case of Natural Language Inference. \textit{Neural Information Processing Systems (NeurIPS)}, 2021.

Udit Arora, William Huang and \textbf{He He}. Types of Out-of-Distribution Texts and How to Detect Them. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2021.

Vishakh Padmakumar and \textbf{He He}. Unsupervised Extractive Summarization with Pointwise Mutual Information. \textit{The European Chapter of the Association for Computational Linguistics (EACL)}, 2021.

Richard Yuanzhe Pang and \textbf{He He}. Text Generation by Learning from Demonstrations. \textit{International Conference on Learning Representations (ICLR)}, 2021.

Esin Durmus, \textbf{He He} and Mona Diab. FEQA: A Question Answering Evaluation Framework for Faithfulness Assessment in Abstractive Summarization. \textit{Association for Computational Linguistics (ACL)}, 2020.

\textbf{He He}$^*$, Nanyun Peng$^*$ and Percy Liang. Pun Generation with Surprise. \textit{North American Chapter of the Association for Computational Linguistics (NAACL)}, 2019.

Yiheng Zhou, \textbf{He He}, Alan Black and Yulia Tsvetkov. A Dynamic Strategy Coach for Effective Negotiation. \textit{Special Interest Group on Discource and Dialogue (SigDial)}, 2019.

\textbf{He He}, Derek Chen, Anusha Balakrishnan and Percy Liang. Decoupling Strategy and Generation in Negotiation Dialogues. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2018.

Eunsol Choi$^*$, \textbf{He He}$^*$, Mohit Iyyer$^*$, Mark Yatskar$^*$, Wen-tau Yih, Yejin Choi, Percy Liang and Luke Zettlemoyer. QuAC: Question Answering in Context. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2018.

Urvashi Khandelwal, \textbf{He He}, Peng Qi and Dan Jurafsky. Sharp Nearby, Fuzzy Far Away: How Neural Language Models Use Context. \textit{Association for Computational Linguistics (ACL)}, 2018.

Juncen Li, Robin Jia, \textbf{He He} and Percy Liang. Delete, Retrieve, Generate: a Simple Approach to Sentiment and Style Transfer. \textit{North American Chapter of the Association for Computational Linguistics (NAACL)}, 2018.

\textbf{He He}, Anusha Balakrishnan, Mihail Eric and Percy Liang. Learning Symmetric Collaborative Dialogue Agents with Dynamic Knowledge Graph Embeddings. \textit{Association for Computational Linguistics (ACL)}, 2017.

Kai-Wei Chang, \textbf{He He}, Hal Daum\'e III, John Langford and St\'ephane Ross. Credit Assignment Compiler for Joint Prediction. \textit{Neural Information Processing Systems (NeurIPS)}, 2016.

\textbf{He He}, Jordan Boyd-Graber, Kevin Kwok and Hal Daum\'e III. Opponent Modeling in Deep Reinforcement Learning. \textit{International Conference on Machine Learning (ICML)}, 2016.

\textbf{He He}, Jordan Boyd-Graber and Hal Daum\'e III. Interpretese vs. Translationese: The Uniqueness of Human Strategies in Simultaneous Interpretation. \textit{North American Chapter of the Association for Computational Linguistics (NAACL)}, 2016.

Xi Chen, \textbf{He He} and Larry Davis. Object Detection in 20 Questions. \textit{Winter Conference on Applications of Computer Vision (WACV)}, 2016.

\textbf{He He}, Alvin Grissom II, John Morgan, Jordan Boyd-Graber and Hal Daum\'e III. Syntax-based Rewriting for Simultaneous Machine Translation. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2015.

Xiangyang Liu, \textbf{He He} and John Baras. Crowdsourcing with Multi-Dimensional Trust. \textit{International Conference on Information Fusion (Fusion)}, 2015.

Xiangyang Liu, \textbf{He He} and John Baras. Trust-Aware Optimal Crowdsourcing With Budget Constraint. \textit{International Conference on Communications (ICC)}, 2015.

Lihong Li, \textbf{He He} and Jason D. Williams. Temporal Supervised Learning for Inferring a Dialog Policy from Example Conversations. \textit{Spoken Lanugage Technology Workshop (SLT)}, 2014.

\textbf{He He}, Hal Daum\'e III and Jason Eisner. Learning to Search in Branch and Bound Algorithms. \textit{Neural Information Processing Systems (NeurIPS)}, 2014.

Alvin Grissom II, \textbf{He He}, John Morgan, Jordan Boyd-Graber and Hal Daum\'e III. Don't Until the Final Verb Wait: Reinforcement Learning for Simultaneous Machine Translation. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2014.

\textbf{He He}, Hal Daum\'e III and Jason Eisner. Dynamic Feature Selection for Dependency Parsing. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2013.

\textbf{He He}, Hal Daum\'e III and Jason Eisner. Imitation Learning by Coaching. \textit{Neural Information Processing Systems (NeurIPS)}, 2012.

Jordan Boyd-Graber, Brianna Satinoff, \textbf{He He} and Hal Daum\'e III. Besting the Quiz Master: Crowdsourcing Incremental Classification Games. \textit{Empirical Methods in Natural Language Processing (EMNLP)}, 2012.

\textbf{He He} and Wan-Chi Siu. Single Image Super-resolution using Gaussian Process Regression. \textit{Computer Vision and Pattern Recognition (CVPR)}, 2011.

\textbf{He He} and Ali Ghodsi. Rare Class classification with SVM. \textit{International Conference on Pattern Recognition (ICPR)}, 2010.

