\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{helvet}

\begin{document}

\name{He He \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{4in}}
Gates 254             & Phone: (301) 312-5903 \\            
Stanford University   & E-mail: hehe@cs.stanford.edu \\         
Stanford, CA 94305    & Website: \url{http://www.umiacs.umd.edu/~hhe}\\        
\end{tabular}

\section{\sc Employment}
{\bf Stanford University}, U.S.A.\\
Postdoc (Supervisor: Percy Liang) \hfill 2016--Present

\section{\sc Education}
{\bf University of Maryland, College Park}, U.S.A.\\
Ph.D. in Computer Science (Advisors: Hal Daum\'e III, Jordan Boyd-Graber) \hfill 2016\\
%\hfill GPA: 3.8/4.0\\
M.Sc. in Computer Science \hfill 2013

{\bf The Hong Kong Polytechnic University}, China\\ 
B.Eng. (Hons) in Electronic and Information Engineering (Advisor: Wan-Chi Siu) \hfill 2011 %\\
% \hfill GPA: 4.0/4.0
%Applied Mathematics Minor

{\bf University of Waterloo}, Canada \hfill Fall 2009\\
Non-degree exchange, Department of Electrical and Computer Engineering %\hfill GPA: 95.2/100

\section{\sc Publications}
{\bf\underline{Conference}}

Kai-Wei Chang, {\bf He He}, Hal Daum\'e III, John Langford and St\'ephane Ross.\\
{\bf Opponent Modeling in Deep Reinforcement Learning.}\\
Neural Information Processing Systems (NIPS), 2016. 

{\bf He He}, Jordan Boyd-Graber, Kevin Kwok and Hal Daum\'e III.\\
{\bf Opponent Modeling in Deep Reinforcement Learning.}\\
International Conference on Machine Learning (ICML), 2016.

{\bf He He}, Jordan Boyd-Graber and Hal Daum\'e III.\\
{\bf Interpretese vs. Translationese: The Uniqueness of Human Strategies in Simultaneous Interpretation.}\\
North American Association for Computational Linguistics (NAACL), 2016.%\\[.1in]

Xi Chen, {\bf He He}, Larry Davis.\\
{\bf Object Detection in 20 Questions.}\\
IEEE Winter Conference on Applications of Computer Vision (WACV), 2016.%\\[.10in]

Jordan Boyd-Graber, Mohit Iyyer, {\bf He He}, and Hal Daum\'e III.\\
{\bf Interactive Incremental Question Answering.} (demo)\\
Neural Information Processing Systems (NIPS), 2015. 
Best demonstration award.
%{\bf \color{red} Best demonstration award}%\\[.10in]

{\bf He He}, Alvin Grissom II, Jordan Boyd-Graber and Hal Daum\'e III.\\
{\bf Syntax-based Rewriting for Simultaneous Machine Translation.}\\
Empirical Methods in Natural Language Processing (EMNLP), 2015.%\\[.10in]

Xiangyang Liu, {\bf He He} and John Baras.\\
{\bf Crowdsourcing with Multi-Dimensional Trust.}\\
International Conference on Information Fusion (Fusion), 2015.
2nd runner-up for the Tammy L. Blair Award.
%{\bf \color{red} 2nd runner-up for the Tammy L. Blair Award}.%\\[.05in]

Xiangyang Liu, {\bf He He} and John Baras.\\
{\bf Trust-Aware Optimal Crowdsourcing With Budget Constraint.}\\
IEEE International Conference on Communications (ICC), 2015.%\\[.05in] 

{\bf He He}, Hal Daum\'e III and Jason Eisner. \\
{\bf Learning to Search in Branch and Bound Algorithms.}\\
Neural Information Processing Systems (NIPS), 2014.%\\[.05in]

Alvin Grissom II, {\bf He He}, Jordan Boyd-Graber, John Morgan, and Hal Daum\'e III. \\
{\bf Don't Until the Final Verb Wait: Reinforcement Learning for Simultaneous Machine Translation.}\\
Empirical Methods in Natural Language Processing (EMNLP), 2014.%\\[.05in]

Lihong Li, {\bf He He} and Jason D. Williams. \\
{\bf Temporal Supervised Learning for Inferring a Dialog Policy from Example Conversations.}\\
Spoken Language Technology Workshop (SLT), 2014.%\\[.05in]

{\bf He He}, Hal Daum\'e III and Jason Eisner.\\
{\bf Dynamic Feature Selection for Dependency Parsing.}\\ 
Empirical Methods in Natural Language Processing (EMNLP), 2013.%\\[.05in]

{\bf He He}, Hal Daum\'e III and Jason Eisner.\\
{\bf Imitation Learning by Coaching.}\\ 
Neural Information Processing Systems (NIPS), 2012.%\\[.05in]

Jordan Boyd-Graber, Brianna Satinoff, {\bf He He} and Hal Daum\'e III.\\
{\bf Besting the Quiz Master: Crowdsourcing Incremental Classification Games.}\\
Empirical Methods in Natural Language Processing (EMNLP), 2012.%\\[.05in]

{\bf He He} and Wan Chi Siu. \\
{\bf Image Super-resolution using Gaussian Process Regression.}\\
Computer Vision and Pattern Recognition Conference (CVPR), 2011.%\\[.05in]

{\bf He He} and Ali Ghodsi. \\
{\bf Rare Class Classification by Support Vector Machine.}\\
International Conference on Pattern Recognition (ICPR), 2010.

{\bf\underline{Workshop}}

{\bf He He}, Paul Mineiro and Nikos Karampatziakis. \\
{\bf Active Information Acquisition.}\\
Machine Learning From and For Adaptive User Technologies: From Active Learning \& Experimentation to Optimization \& Personalization, NIPS, 2015.%\\[.05in]

%Xi Chen, {\bf He He} and Larry Davis. \\
%{\bf Search for Objects in 20 Questions.}\\
%Scene Understanding Workshop, CVPR, 2015.%\\[.05in]

{\bf He He}, Hal Daum\'e III and Jason Eisner.\\
{\bf Cost-sensitive Dynamic Feature Selection.}
Workshop on Inferning, ICML, 2012.

\section{\sc Awards}
Larry S. Davis Dissertation Award \hfill 2016\\
NIPS Student Travel Award \hfill 2012, 2014\\
Dean's Fellowship, UMD \hfill 2011, 2012 \\
Best Academic Performance Award (awarded to the top 3 students), HKPolyU \hfill 2008 - 2010\\
Dean's Honors List, HKPolyU \hfill 2008 - 2010\\
Non-local Students Scholarship (academic), HKPolyU \hfill 2007 - 2010\\
HSBC Scholarship for Mainland Students \hfill 2008 - 2010\\
CMA \& Donors Scholarship \hfill 2008 - 2010

%
\section{\sc Working Experience} 
{\bf Microsoft Cloud Information and Service Lab}, Redmond, WA\\
\emph{Research Intern} (mentors: Paul Mineiro, Nikos Karampatziakis) \hfill June 2015 to August 2015\\
Active information acquisition for sentiment analysis and object recognition 
%\vspace*{-.1in}
%\begin{list1}
%\item[] Active information acquisition for sentiment analysis and object recognition 
%\end{list1}

{\bf Machine Learning Group, Microsoft Research}, Redmond, WA\\
\emph{Research Intern} (mentors: Lihong Li, Jason Williams) \hfill May 2013 to August 2013\\
Combining imitation learning and reinforcement learning for dialog management 
%\vspace*{-.1in}
%\begin{list1}
%\item[] Combining imitation learning and reinforcement learning for dialog management 
%\end{list1}

%\section{\sc Research Experience}
%{\bf Computational Linguistics and Information Processing Lab, University of Maryland, College Park}\\
%\emph{Research Assistant} (advisor: Dr. Hal Daum\'e III) \hfill October 2011 to present\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Sequential decision-making for natural language processing 
%\end{list1}
%%
%{\bf Center for Multimedia Signal Processing, The Hong Kong Polytechnic University}\\
%\emph{Final Year Project} (advisor: Prof. Wan-Chi Siu) \hfill August 2010 to July 2011\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Single image super-resolution 
%\end{list1}
%%
%{\bf Center for Language and Speech Processing, Johns Hopkins University}\\
%\emph{Workshop} (advisors: Dr. Jan Neumann, Prof. Jana Kosecka) \hfill June 2010 to July 2010\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Object detection and action recognition
%\end{list1}
%
%{\bf Department of Computing, The Hong Kong Polytechnic University}\\
%\emph{Research Assistant} (advisor: Prof. Keith C. C. Chan) \hfill January 2010 to May 2010\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Analyzed algorithms for Gene Regulatory Network reconstruction (recurrent neural network, dynamic Bayesian network and fuzzy dependency relationship)
%\item[] Developed genetic programming algorithms for topology recovery of gene regulatory networks
%\item[] Used averaging to reinforce the grouping effect in regularized linear regression for variable selection
%\end{list1}
%
%{\bf Department of Statistics and Actuarial Science, University of Waterloo}\\
%\emph{Course Project} (advisor: Prof. Ali Ghodsi) \hfill Fall 2009\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Improved SVM's performance with imbalanced datasets by modifying optimization constraints  
%\end{list1}
%%
%{\bf Centre for Multimedia Signal Processing, The Hong Kong Polytechnic University}\\
%\emph{Undergraduate Research Program} (advisor: Prof. Kenneth K. M. Lam) \hfill Summer 2009\\
%\vspace*{-.1in}
%\begin{list1}
%\item[] Implemented Adaboost for \emph{Robust Real-Time Face Detection} (P. Viola and M. J. Jones, 2004)
%\end{list1}
\section{\sc Teaching Experience} 
%{\bf Department of English, The Hong Kong Polytechnic University}\\
%  English tutoring service for young children \hfill December 2008
%  
%{\bf Student Affair Office, The Hong Kong Polytechnic University}\\
%  Peer tutor in Physics \hfill Fall 2008
{\bf Department of Linguistics, University of Maryland, College Park}\\
  \emph{Co-instructor}, Python Crash Course at the Winter Storm Workshop \hfill Jan 2013

{\bf Department of Computer Science, University of Maryland, College Park}\\
  \emph{Teaching Assistant}, CMSC 132 Object-oriented Programming \hfill Fall 2011
  
%\section{\sc Technical Skills}
%Java, C/C++, Python, Matlab, Unix/Linux, HTML, \LaTeX

\section{\sc Service}
{\bf\underline{Organizer}}

NAACL Workshop: Human-computer question answering, 2016.\\
With Jordan Boyd-Graber, Mohit Iyyer and Hal Daum\'e III.

NAACL Tutorial: Hands-on Learning to Search for Structured Prediction, 2015.\\
With Hal Daum\'e III, John Lanford, Kai-Wei Chang and Sudha Rao.

Mid-Atlantic Student Colloquium on Speech, Language and Learning, 2015.\\
With Mossaab Bagdouri, Shuoyang Ding and Nanyun Peng, advised by Hal Daum\'e III and Mark Dredze.

DARPA Program: Probabilistic Programming for Advancing Machine Learning (Challenge Problem 5: Natural Language Processing), 2015.\\
With Galois, Inc. and Tom Dietterich.

{\bf\underline{Co-chair}}

ACL Student Research Workshop, 2016

{\bf\underline{Reviewer}}

NAACL, EMNLP, ACL, NIPS, ICML, AAAI, AISTATS
%NAACL 2016, ICML 2016, EMNLP 2015--2016, NIPS 2014--2016

\end{resume}
\end{document}




