\documentclass[a4paper,11pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{url,parskip}     %other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo}                 %better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular}                 %for Grades
\usepackage{titlesec}                    %custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tgtermes}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

%--------------------SECTIONS-----------------------------------
\section{Publications}
{\underline{Refereed conference papers}}

{\bf He He}, Anusha Balakrishnan, Mihail Eric and Percy Liang.\\
{\bf Learning Symmetric Collaborative Dialogue Agents with Dynamic Knowledge Graph Embeddings.}\\
Association for Computational Linguistics (ACL), 2017\\
\\
{\bf He He}, Jordan Boyd-Graber, Kevin Kwok and Hal Daum\'e III.\\
{\bf Opponent Modeling in Deep Reinforcement Learning.}\\
International Conference on Machine Learning (ICML), 2016.\\
\\
Kai-Wei Chang, {\bf He He}, Hal Daum\'e III, John Langford and St\'ephane Ross.\\
{\bf A Credit Assignment Compiler for Joint Prediction.}\\
Neural Information Processing Systems (NIPS), 2016.\\ 
\\
{\bf He He}, Jordan Boyd-Graber and Hal Daum\'e III.\\
{\bf Interpretese vs. Translationese: The Uniqueness of Human Strategies in Simultaneous Interpretation.} (Short paper)\\
North American Association for Computational Linguistics (NAACL), 2016.\\
\\
Xi Chen, {\bf He He}, Larry Davis.\\
{\bf Object Detection in 20 Questions.}\\
IEEE Winter Conference on Applications of Computer Vision (WACV), 2016.\\
\\
{\bf He He}, Alvin Grissom II, Jordan Boyd-Graber and Hal Daum\'e III.\\
{\bf Syntax-based Rewriting for Simultaneous Machine Translation.}\\
Empirical Methods in Natural Language Processing (EMNLP), 2015.\\
\\
Jordan Boyd-Graber, Mohit Iyyer, {\bf He He}, and Hal Daum\'e III.\\
{\bf Interactive Incremental Question Answering.} (Demonstration track)\\
Neural Information Processing Systems (NIPS), 2015. 
Best demonstration award.\\
\\
Xiangyang Liu, {\bf He He} and John Baras.\\
{\bf Crowdsourcing with Multi-Dimensional Trust.}\\
International Conference on Information Fusion (Fusion), 2015.
Tammy L. Blair Award 2nd runner-up.\\
\\
Xiangyang Liu, {\bf He He} and John Baras.\\
{\bf Trust-Aware Optimal Crowdsourcing With Budget Constraint.}\\
IEEE International Conference on Communications (ICC), 2015.\\
\\
{\bf He He}, Hal Daum\'e III and Jason Eisner. \\
{\bf Learning to Search in Branch and Bound Algorithms.}\\
Neural Information Processing Systems (NIPS), 2014.\\
\\
Alvin Grissom II, {\bf He He}, Jordan Boyd-Graber, John Morgan, and Hal Daum\'e III. \\
{\bf Don't Until the Final Verb Wait: Reinforcement Learning for Simultaneous Machine Translation.}\\
Empirical Methods in Natural Language Processing (EMNLP), 2014.\\
\\
Lihong Li, {\bf He He} and Jason D. Williams. \\
{\bf Temporal Supervised Learning for Inferring a Dialog Policy from Example Conversations.}\\
IEEE Workshop on Spoken Language Technology (SLT), 2014.\\
\\
{\bf He He}, Hal Daum\'e III and Jason Eisner.\\
{\bf Dynamic Feature Selection for Dependency Parsing.}\\ 
Empirical Methods in Natural Language Processing (EMNLP), 2013.\\
\\
{\bf He He}, Hal Daum\'e III and Jason Eisner.\\
{\bf Imitation Learning by Coaching.}\\ 
Neural Information Processing Systems (NIPS), 2012.\\
\\
Jordan Boyd-Graber, Brianna Satinoff, {\bf He He} and Hal Daum\'e III.\\
{\bf Besting the Quiz Master: Crowdsourcing Incremental Classification Games.}\\
Empirical Methods in Natural Language Processing (EMNLP), 2012.\\
\\
{\bf He He} and Wan-Chi Siu. \\
{\bf Image Super-resolution using Gaussian Process Regression.}\\
Computer Vision and Pattern Recognition Conference (CVPR), 2011.\\
\\
{\bf He He} and Ali Ghodsi. \\
{\bf Rare Class Classification by Support Vector Machines.}\\
International Conference on Pattern Recognition (ICPR), 2010.\\
\\
{\underline{Workshop papers and manuscripts}}

{\bf He He}, Paul Mineiro and Nikos Karampatziakis. \\
{\bf Active Information Acquisition.}\\
Machine Learning From and For Adaptive User Technologies: From Active Learning \& Experimentation to Optimization \& Personalization, NIPS, 2015.\\
\\
Kai-Wei Chang, {\bf He He}, Hal Daum\'e III and John Langford.\\
{\bf Learning to Search for Dependencies.}\\
Arxiv 1503.05615, 2015.\\
\\
{\bf He He}, Hal Daum\'e III and Jason Eisner.\\
{\bf Cost-sensitive Dynamic Feature Selection.}\\
Workshop on Inferning, ICML, 2012.

\end{document}

